Open-source landscape for 3D CSEM modelling

### 2020-09-16 manuscript/Manuscript.tex
Marlim figures and captinos

The block model is a derivation of the \emph{Dublin Test Model 1} from the first EM modelling workshop described by \cite{GJI.13.Miensopust}. We use the same layout of the blocks but adjust the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:model-block}. Additionally, we add our \emph{Layered Model} as a VTI background. The three resistive blocks have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$ (cube, North-West).
%
\plot*{model-block}{width=.6\textwidth}{
  Sketch of the block model, consisting of the layered background model with three resistive blocks, embedded in the thick background layer which has VTI with $\lambda=\sqrt{2}$.
}
%

@@

\subsection{Marlim R3D}

@@

%
\plot*{model-marlim}{width=\textwidth}{
  This figure obviously needs to be improved massively (at least a colorbar).
  What would you like to show from the actual data here?
  A nice figure would  be Figure 2 in the original paper; however, note that
  the drawn survey line in that figure are plainly wrong.
  \textbf{Air, water, and salt are isotropic, rest has $\lambda=\sqrt{2}$.}
}
%

@@

%
\plot*{results-marlim-responses}{width=\textwidth}{
}
%

%
\plot*{results-marlim_2published}{width=\textwidth}{
  This is one heck of a figure. Just an idea, please make suggestions how to
  improve it (currently, \petgem data is a copy of \custem data, and \simpeg
  data is a copy of \emg3d data).
}
%

%
\plot*{results-marlim_2ours}{width=\textwidth}{
}
%

%
\plot*{results-marlim_entire}{width=\textwidth}{
}
%
%
\plot*{results-marlim_survey}{width=\textwidth}{
}
%

@@

\clearpage~\newpage
\itodo{HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE}
\section{TODOs}

>>>>

The block model is a derivation of the \emph{Dublin Test Model 1} from the first EM modelling workshop described by \cite{GJI.13.Miensopust}. We use the same layout of the blocks but adjust the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:model-block}. Additionally, we add our \emph{Layered Model} as a VTI background. The three resistive blocks have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$ (cube, North-West).
%
\plot*{model-block}{width=.6\textwidth}{Sketch of the block model, consisting of the layered background model with three resistive blocks, embedded in the thick background layer which has VTI with $\lambda=\sqrt{\rho_\textrm{v}/\rho_\textrm{h}}=\sqrt{2}$.}
%

@@

\clearpage
\itodo{HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE}
\subsection{Marlim R3D}

@@

%
\plot*{model-marlim}{width=\textwidth}{Marlim horizontal resistivity model, $x$-$z$-slice through the receiver $y$-position. Air (not shown in the model), seawater, and the salt body are electrically isotropic, everything else has a VTI with $\lambda=\sqrt{2}$.}
%

@@

%
\plot*{results-marlim-responses}{width=\textwidth}{Marlim R3D comparison between our codes (grey lines) and the published data (coloured lines). The grey lines under the coloured lines are not visible in most areas, meaning they are very similar. However, there are three notable zones, (1) to (3), which are explained further in the text.}
%

%
\plot*{results-marlim_2published}{width=\textwidth}{NRMSDs for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively. Shown are the three frequencies 0.125\,Hz, 0.5\,Hz, and 1.0\,Hz in the top, middle, and bottom row, respectively.}
%

%
\plot*{results-marlim_2ours}{width=\textwidth}{NRMSDs, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other. Good visible is that \custem and \petgem produce very similar results, which is due to the fact that they use the same mesh.}
%

%
\plot*{results-marlim_entire}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the entire computational domain.}
%

%
\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain.}
%

@@

\section{TODOs}
